A review on Generative Learning in Computer Vision

### 2020-05-04 paper.tex
update intro and started lit review

In 2014, Goodfellow et al. published a paper on Generative Adversarial Networks (GANs) \cite{b1}. GANs has since then been applied in numerous fields including Natural Language Processing (NLP) and computer vision. This family of deep learning methods has become quite popular due to its good results. In this review paper provides a survey on recent adaptations of GAN alongwith the first-original version often called as vanilla GAN.

@@

\section{Literature Review}
\label{lr}

>>>>

With such advancements, the need for data is never ending. CV models running on neural networks require huge amount labeled training data to train them. But the problem lies in finding suitable high-quality data. Manual scavenging and labelling of data is not an ideal approach as it is costly to do so. The only option left for computer scientists is to produce high quality artificial data either from scratch or by manipulating existing data. Generative learning is one such popular way to generate artificial data. In this paper, we will look at different generative methods introduced lately.

@@

\section{Literature Review}
\label{lr}
In 2014, Goodfellow et al. published a paper on Generative Adversarial Networks (GANs) \cite{b1}. GANs has since then been applied in numerous fields including Natural Language Processing (NLP) and computer vision. This family of deep learning methods has become quite popular due to its good results. In this review paper provides a survey on recent adaptations of GAN alongwith the first-original version often called as vanilla GAN.
